Lattice Boltzmann simulations of magnetically responsive\\ anisotropic particle stabilized emulsions

### 2025-03-04 chapters/LBM_technique.tex
Changes 1. Changed chapter 2 content 2. Addeed chapter 1 curvature results

For particles close to contact, meaning with inter-surface distances under 1 lattice unit the hydrodynamics are unresolved as the
distance is smaller than what the model can resolve. Lubrication forces are added to reduce the likelihood of particle overlap. For 
spherical particles, this is defined in Equation \ref{eq:sphere_lube}

@@

where $R_i$ and $R_j$ are the radii of each particle involved in the interaction, $\vec{r}_{ij}$ is the distance
vector between the particle centers, $\mathbf{u}_{ij}$ are the relative velocities of the particles and $\Delta_c$ 
is the cutoff distance when the lubrication force begins to act. If particles are able to overcome the lubrication forces, 
a hertzian contact force is also added to ensure that there is no particle overlap, defined in Equation \ref{eq:hertz_def}

>>>>

For particles close to contact, meaning with inter-surface distances under 1 lattice unit the hydrodynamics are unresolved as the
distance is smaller than what the model can resolve. Lubrication forces are added to reduce the likelihood of particle overlap. For 
spherical particles, this is defined in Equation \eqref{eq:lubrication}

@@

where $R_i$ and $R_j$ are the radii of each particle involved in the interaction, $\vec{r}_{ij}$ is the distance
vector between the particle centers, $\mathbf{u}_{ij}$ are the relative velocities of the particles and $\Delta_c$ 
is the cutoff distance when the lubrication force begins to act. If particles are able to overcome the lubrication forces, 
a hertzian contact force is also added to ensure that there is no particle overlap, defined in Equation \eqref{eq:hertz}

### 2025-03-04 chapters/paper1.tex
Changes 1. Changed chapter 2 content 2. Addeed chapter 1 curvature results

\section{Results}\label{sec:results}

@@

\begin{figure} 
    \centering 
    \includegraphics[width=\textwidth]{figures/results/paper1/curvature_vs_coverage.png} 
    \caption{Plots of Gaussian $\langle K \rangle \Sigma^{-2}$ curvature over time averaged across 3 runs. 
    From left to right, we have particles with $\alpha = 0.5, 1, 2$. We observe that the initial stages of 
    evolution are unaffected by the applied magnetic field. However, after about 10000 timsteps, we see a 
    magnetic field dependence on the evolution of the Gaussian curvature. The preservation of this divergence 
    occurs when ellipsoidal particles are used but not spherical particles.} 
    \label{fig:curvature_vs_coverage}
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[width=\columnwidth]{figures/results/paper1/Q6_vs_coverage.png} 
    \caption{Time dependence of the mean six fold symmetry parameter, $\langle Q6 \rangle$ for bijels 
    stabilized with oblate(left), spherical(middle) and prolate(right) particles. We show that spherical 
    particles posess the hexagonal close packing structure for particles on interfaces. Ellipsoidal particles 
    however posess behavior that is magnetic field and particle aspect ratio dependent.} 
    \label{fig:Q6_coverage} 
\end{figure}

>>>>

\section{Results}\label{sec:results_p1}

@@

\begin{figure} 
    \centering 
    \includegraphics[width=\textwidth]{figures/results/paper1/genus_curvature_vs_coverage.png} 
    \caption{Plots of Gaussian $\langle K \rangle \Sigma^{-2}$ curvature over time averaged across 3 runs. 
    From left to right, we have particles with $\alpha = 0.5, 1, 2$. We observe that the initial stages of 
    evolution are unaffected by the applied magnetic field. However, after about 10000 timsteps, we see a 
    magnetic field dependence on the evolution of the Gaussian curvature. The preservation of this divergence 
    occurs when ellipsoidal particles are used but not spherical particles.} 
    \label{fig:curvature_vs_coverage}
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[width=\columnwidth]{figures/results/paper1/steinhardt_vs_coverage.png} 
    \caption{Time dependence of the mean six fold symmetry parameter, $\langle Q6 \rangle$ for bijels 
    stabilized with oblate(left), spherical(middle) and prolate(right) particles. We show that spherical 
    particles posess the hexagonal close packing structure for particles on interfaces. Ellipsoidal particles 
    however posess behavior that is magnetic field and particle aspect ratio dependent.} 
    \label{fig:Q6_coverage} 
\end{figure}
